### 2018-05-17 Paper/examples.tex
.
..

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left:Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
borehole discharge function in~\eqref{eq:bore}. Right: 
Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_bore}
\end{center}
\end{figure}

@@

\caption{Description and distributions of uncertain parameters in the limit state function
given by~\eqref{eq:limit}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
mean, $\mu$ and variance, $\sigma^2$. $\mathcal{U}[a,b]$ denotes a uniform distribution
with limits $a$ and $b$.}
\label{tab:osc}
\end{table}

>>>>

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
borehole discharge function in~\eqref{eq:bore}. Right: 
Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_bore}
\end{center}
\end{figure}

@@

\caption{Description and distributions of uncertain parameters in the limit state function
given by~\eqref{eq:limit}. $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with
mean, $\mu$ and variance, $\sigma^2$.}
\label{tab:osc}
\end{table}
